Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-11-11 paper.tex
Finished discussion

A few limitations remain that should be addressed in the
future. When

\begin{itemize}
\item Security: containers may be updated after being integrated in the platforms.
\item Testing of applications.
\end{itemize}

>>>>

A few limitations remain that should be addressed in the
future. First, \boutiques moves the application porting bottleneck to
validation. Using \boutiques, functions can be automatically exported
from frameworks such as Nipype and SPM, creating hundreds of richly
described applications potentially usable by end-users. However, how
to validate that these applications actually execute as expected
remain unclear. A testing framework could be designed and potentially
fed by existing frameworks, to address this issue.

Another limitation is related to the security of containerized
applications. Since containers are usually controlled by application
developers rather than platforms, which is a good thing to reduce
application porting bottlenecks, nothing prevents developers to embed
malicious code in their container at any stage of the process,
possibly after a platform administrator inspected the
container. Containers are currently bulky file archives that are
cumbersome to inspect. Tools need to be developed to allow for an
easier characterization of container contents, for instance through
comparison digests with respect to validated base images.
